Political Support in the United States

### 2024-03-17 paper/paper.qmd
Update paper.qmd

@@

```

>>>>

In this paper, we performed a logistic regression model from our cleaned dataset, which analysis 500 observations. Our focus of this paper was relationship of presidential candidate voted by individuals between the races (raceBlack, raceHispanic, raceMiddle Eastern, raceNative American, raceOther, raceTwo or more races, raceWhite) and the reference group, raceAsian.

@@

```
The coefficient represents the logarithm of the anticipated variance in backing for Biden in contrast to Trump. When the coefficient values are negative, which means the voters decrease their support in Biden. Whereas, when the values are greater and equal to zero (positive) meaning the voters increase their support for Biden.

From the @tbl-model-summary-tableLogistic, with the constant variable, raceAsian, the intercept is -0.462 which means that the support for Biden decreases by about 0.784 units while all other variables remain the same. The following race, Hispanic (0.354), Middle Eastern (0.535), White (0.940), Native American (1.245), Two or more races (1.372) has stronger/ increasing their support for stronger/ increasing their support for Biden; in this case, the mixed race people have the strongest support for Biden. Yet, Black (−1.030) and Other  (−0.092) decrease support for Biden by looking at the coefficients.
